---
title       : 
subtitle    : 
author      : 
job         : 
framework   : landslide        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Purpose of Application

* Analyses data from all soccer matches of the national teams since 1930.
* The application is accessible online here: https://efsa.shinyapps.io/soccerAnalytics/


---



## Data
```{r echo=FALSE,results='hide',message=FALSE}
source("../analysis.r")
games <- loadData()
countryStats <- countryStats("DEU",games)
```

* data set of 7560 football matches 
* from 1930 onward
* all big tournaments

---

## Features of application
The application has the following features:

* Selection of country via drop down
* Dynamic update of 4 different statistics
   + Over all goals of the country
   + histogram of the distribution of the  umber of goals
   + Overall points (0 for loss, 1 for draw,2 for win) of the country
   + Distribution of the match results

---

## Usage example
Do see the statistics for country "DEU" (= Germany):

* The user selects "DEU" in the drop down 
* -> Statistics of selected country get updated


---


## Screenshot of a plot with the goals distribution for Germany
```{r echo=FALSE,warning=F}
plot(table(countryStats$goals),lwd = 20,xlab = "Goals",ylab = "Frequency",
         col="blue",
         main = "Frequency of goals"
         )
```








